### 2018-07-28 paper/article.tex
Clean-up

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/datasets.csv}{}%
	{

@@

The full implementation of the proposed method and the script allowing the repetition of the presented research may be found in the git repository available at \url{url-removed-due-to-} \url{blind-review}.

@@

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/summary.csv}{}%
	{\clf &
	\full & \us & \os &
	\withoutos & \withos & 
	\withoutpru & \withpru &
	\reg & \wei & \con & \nor & \nci

>>>>

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{datasets.csv}{}%
	{

@@

The full implementation of the proposed method, content of the following paper and the script allowing the repetition of the presented research may be found in the git repository\footnote{\url{https://github.com/w4k2/umce}}.

@@

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{summary.csv}{}%
	{\clf &
	\full & \us & \os &
	\withoutos & \withos & 
	\withoutpru & \withpru &
	\reg & \wei & \con & \nor & \nci
